\section{Annotation Guidelines Summary}
\label{app:guidelines}

Each sentence is labelled as suggestion~(1) or
non-suggestion~(0). The core decision rule is: ``Does this
sentence propose a concrete action the hotel could take to
improve?'' Guidelines cover six edge-case categories:

\begin{enumerate}
  \item \textbf{Wishes and desires} (label~1): ``I wish the pool
  was open later'' implies extending pool hours.
  \item \textbf{Implicit comparisons} (label~1): ``Other hotels
  offer free shuttle'' implies adding a shuttle service.
  \item \textbf{Conditional praise} (label~1): ``Great hotel, but
  they need to fix the elevators'' contains an actionable clause.
  \item \textbf{Complaints without direction} (label~0): ``The
  check-in took over an hour'' describes a problem without
  proposing a fix.
  \item \textbf{Positive modals} (label~0): ``I would definitely
  stay again'' uses ``would'' for praise, not suggestion.
  \item \textbf{Guest advice} (label~1): ``Try the laksa at the
  food court'' is a recommendation with a directive element.
\end{enumerate}

Guidelines were revised (v1.0 $\rightarrow$ v1.1) after the
calibration round to clarify the complaint-versus-suggestion
boundary and the distinction between informational statements
and guest-directed advice.

\section{Code Availability}
\label{app:code}

All code, data processing scripts, and trained model checkpoints
are available at
\url{https://github.com/LanscorTK/NLP_Team6}. The full
pipeline can be reproduced with
\texttt{python run\_pipeline.py}.

\section{AI Tool Acknowledgement}
\label{app:ai}

We used Claude (Anthropic) as an assistive tool for coding
support and project planning throughout this project. Specific
uses included: debugging Python pipeline code, drafting
boilerplate LaTeX structure, and literature search assistance
via arXiv and Semantic Scholar API integrations. All substantive
research decisions---task formulation, annotation guideline
design, model selection, hyperparameter choices, and
interpretation of results---were made by the team. Claude was
not used to generate report prose; all analytical writing was
authored by team members. This disclosure follows UCL guidance
on acknowledging the use of generative AI tools in assessed
work.
